\cleardoublepage
\phantomsection
\addcontentsline{toc}{section}{References}
\begin{thebibliography}{99}
% We *really* want to break URLs across lines here. Since URL coloring is
% pure black, the printer won't print these links in ``color''. It's also
% important that this line is within the ``thebibliography`` environment,
% because we only want this behavior in the bibliography.
\hypersetup{ocgcolorlinks=false}
\bibitem{amazon-products}
Amazon. 2014. Product Advertising API. [Online]. Available from: \url{https://affiliate-program.amazon.com/gp/advertising/api/detail/main.html}. Accessed 2014 Apr 24.

\bibitem{open-nlp}
Apache Software Foundation. 2010. Welcome to Apache OpenNLP. [Online]. Available from: \url{https://opennlp.apache.org/}. Accessed 2014 Apr 16.

\bibitem{biology}
Avissar Y, Choi J, DeSaix J, Jurukovski V, Wise R, Rye C. 2013. Biology [Online]. 1st. OpenStax College. Available from: \url{http://goo.gl/hKHVhZ}. Accessed 2014 Feb 20.

\bibitem{nlpwp}
Bird S, Klein E, Loper E. Natural Language Processing with Python. 1st ed. Beijing: O'Reilly; 2009.

\bibitem{bowker}
Bowker. 2011. New Book Titles and Editions, 2002--2011. [Online]. Available from: \url{http://www.bowker.com/assets/downloads/products/isbn_output_2002-2011.pdf}. Accessed 2014 Mar 1.

\bibitem{macrex}
Calvert D, Calvert H. 2014. Macrex. [Online]. Available from: \url{http://www.macrex.com}. Accessed 2014 April 8.

\bibitem{connolly}
Connolly D. 2010. How to Contract with a Book Indexer or "Hi, Can You Do an Index for Me in Three Days?" [Online]. Available from: \url{http://www.wfwbooks.com/howto.htm}. Accessed 2014 Mar 1.

\bibitem{google-books}
Google. 2014. Google Books. [Online]. Available from: \url{http://books.google.com}. Accessed 2014 Apr 24.

\bibitem{google-nlp}
Google. 2014. Research at Google: Natural Language Processing. [Online]. Available from: \url{http://research.google.com/pubs/NaturalLanguageProcessing.html}. Accessed 2014 Mar 1.

\bibitem{jurafsky}
Jurafsky D, Martin JH. Speech and Language Processing. 2nd ed. Upper Saddle River, NJ: Pearson Prentice Hall; 2009.

\bibitem{automatic-indexing}
Korycinski C, Newell AF. Natural-Language Processing and Automatic Indexing. The Indexer [Internet]. 1990 [cited 2013 Apr 22]; 17(1): 21-29. Available from: \url{http://www.theindexer.org/files/17-1/17-1_021.pdf}.

\bibitem{lamport}
Lamport L. 1987. MakeIndex: An Index Processor for \LaTeX. [Online]. Available from: \url{http://www.tex.ac.uk/ctan/indexing/makeindex/doc/makeindex.pdf}. Accessed 2014 April 8.

\bibitem{book-book-goose}
Mason, H. 2013. Book Book Goose. [Online]. Available from: \url{http://www.bookbookgoose.com/}. Accessed 2014 Apr 24.

\bibitem{mediawiki-markup}
MediaWiki. 2014. Help:Formatting. [Online]. Available from: \url{http://www.mediawiki.org/wiki/Help:Formatting}. Accessed 2014 Feb 20.

\bibitem{mediawiki-installation}
MediaWiki. 2014. Manual:Installation guide. [Online]. Available from: \url{http://www.mediawiki.org/wiki/Installation}. Accessed 2014 Feb 20.

\bibitem{mediawiki-import}
MediaWiki. 2014. Manual:Moving a wiki. [Online]. Available from: \url{http://www.mediawiki.org/wiki/Manual:Moving_a_wiki#Import_the_database_backup}. Accessed 2014 Feb 20.

\bibitem{ms-word-indexing}
Microsoft. 2014. Create an Index and Update an Index. [Online]. Available from: \url{http://office.microsoft.com/en-us/word-help/create-an-index-and-update-an-index-HP001226499.aspx}. Accessed 2014 April 8.

\bibitem{mulvany}
Mulvany NC. Indexing Books. 2nd ed. Chicago: The University of Chicago Press; 2005.

\bibitem{nltk}
NLTK. 2014. Natural Language Toolkit. [Online]. Available from: \url{http://www.nltk.org/}. Accessed 2014 Feb 26.

\bibitem{nltk-install}
NLTK. 2014. Installing NLTK. [Online]. Available from: \url{http://www.nltk.org/install.html}. Accessed 2014 Apr 16.

\bibitem{norvig}
Norvig P. How to Write a Spelling Corrector. [Online]. Available from: \url{http://norvig.com/spell-correct.html}. Accessed 2014 Mar 1.

\bibitem{oed-index}
OED Online. index, n. [Online]. Available from: \url{http://www.oed.com/view/Entry/94372}. Accessed 2014 Mar 1.

\bibitem{oed-nlp}
OED Online. natural language processing, n. [Online]. Available from: \url{http://www.oed.com/view/Entry/255272}. Accessed 2014 Mar 1.

\bibitem{openstax-bio}
OpenStax College. 2013 Mar. Biology [Internet]. OpenStax College. Available from: \url{https://openstaxcollege.org/textbooks/biology}. Accessed 2014 Feb 20.

\bibitem{pypi-ranking}
PyPI Ranking. 2014. All Time Package Rankings. [Online]. Available from: \url{http://pypi-ranking.info/alltime}. Accessed 2014 Apr 16.

\bibitem{beautifulsoup}
Richardson L. 2014. Beautiful Soup. [Online]. Available from: \url{http://www.crummy.com/software/BeautifulSoup/}. Accessed 2014 Feb 26.

\bibitem{rish}
Rish, I. An empirical study of the naive Bayes classifier. IJCAI 2001 Workshop on Empirical Methods in Artificial Intelligence [Internet]. 2001 [cited 2014 Apr 14]; 3(22). Available from: \url{http://www.research.ibm.com/people/r/rish/papers/RC22230.pdf}

\bibitem{sky-software}
SKY Software. 2014. Sky Index Professional. [Online]. Available from: \url{http://www.sky-software.com/}. Accessed 2014 Apr 8.

\bibitem{stanford-nlp}
Stanford NLP Group. 2011. Stanford NLP Software. [Online]. Available from: \url{http://nlp.stanford.edu/software/index.shtml}. Accessed 2014 Apr 16.

\bibitem{wiki-exporter}
Wikipedia. 2014. Export pages. [Online]. Available from: \url{http://en.wikipedia.org/wiki/Special:Export}. Accessed 2014 Feb 20.

\bibitem{wikipedia}
Wikipedia. 2014. Wikipedia. [Online]. Available from: \url{http://www.wikipedia.org/}. Accessed 2014 Apr 24.

\bibitem{wiki-disambiguation}
Wikipedia. 2014. Wikipedia:Disambiguation. [Online]. Available from: \url{http://en.wikipedia.org/wiki/Wikipedia:Disambiguation}. Accessed 2014 Feb 26.

\bibitem{wiki-dump-titles}
Wikimedia Foundation. 2013. List of page titles in main namespace. [Online]. Available from: \url{http://dumps.wikimedia.org/enwiki/20131202/enwiki-20131202-all-titles-in-ns0.gz}. Accessed 2014 Feb 20.

\bibitem{wiki-robots}
Wikimedia Foundation. 2014. robots.txt. [Online]. Available from: \url{http://en.wikipedia.org/robots.txt}. Accessed 2014 Apr 1.

\bibitem{wiki-dumps}
Wikimedia Foundation. 2014. Wikimedia Downloads. [Online]. Available from: \url{http://dumps.wikimedia.org/}. Accessed 2014 Feb 20.

\bibitem{bit-of-news}
Xu X. 2013. Bit-of-News: About. [Online]. Available from: \url{http://bitofnews.com/about.html}. Accessed 2014 Mar 1.

\end{thebibliography}